Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-07-19 response_2.txt

Reviewer A

>*The annotation guidelines are needed to ensure replicability. Add them as
appendix material.

We've added them, though we note the guidelines are not really a contribution of this work, much of its content was created as part of Brooke et al. 2015 (though there was some editing, additions, and consolidations, and well as translations into other languages and adaptions to language specific phenomena).

> *In table 5 these examples include a lot of noise. Can the authors comments
how to decide on the criteria for rejecting something as FS.

There is of course some noise, but based on our analysis the noise is fairly consistent with the precision numbers in our evaluation (i.e. most of the ICWSM examples are good FS, whereas about half of the BNC are). Hopefully including the guidelines helps with this, since we don't feel its possible to give succinct explanation of how to decide whether something is an FS: though there are several tests which can help (e.g., can elements be switched out, can the phrase be paraphrased without becoming awkward), at the core we are always reliant on native speaker intuition about whether a sequence of words is produced as a unit, i.e. Wray's definition as given at the beginning Section 2.

Reviewer B

> - For readers familiar with machine learning notation, it would be more
intuitive to use y throughout for the variables to be predicted, namely the
binary activation states of n-gram nodes. It may also be more intuitive to
use x instead of t for each "input" (n-gram node). Then covering could be
defined more explicitly as max{0, (c(x)-\sum_{i \in parents(x)} y_i *
c(x_i))/c(x)}, and likewise for other equations. The optimization problem
could be stated formally by wrapping argmax_{y,C} around eq. (1).

We have integrated the y suggestion, though not quite to the extent you have
suggested, since it creates other issues with the presentation.

>- I was a bit confused about the definition of "overlap" at the type vs.
token level: at first I thought the graph was constructed with each node
having its own corpus frequency information, but there are mentions of
counting overlaps in a corpus, and these counts are presumably associated
with edges between type-overlapping nodes. Showing frequency counts in
figure 2 may help clarify this. From figure 2, I assume at a type level, two
nodes overlap if at least one word is shared between the two n-grams, but
neither set of words is a superset of the other (which would be
subsumption), and a gap counts as a special word for determining subsumption
vs. overlap ("keep everything under wraps" and "keep * under wraps" merely
overlap), but two n-grams must share more than a gap to count as
overlapping. Is the ordering of tokens significant for determining overlap?

We've added some clarification of this point. Overlap at the type level consists
exactly of the count of token overlaps in the corpus. Two n-grams types might 
share words at the type level, but are considered overlapping only when there 
is at least one token in the corpus which belong to an instance of each type.

Related to this, we realized that we had left out the important point that 
subsumed n-grams are considered to trivially overlap with subsuming n-grams 
for the purposes of counting their overlap score when both are on (in addition 
to covering and clearing effects which occur when one of the two nodes is off). 
The reverse, though, is not true, since that would basically prohibit any two 
subsuming nodes from turning on (since the count of subsumed node is always larger
than the subsuming one).

Reviewer B

> - In some place, the paper is not an easy read -- I found a few
expressions that were fairly cryptic even for a seasoned reviewer in
NLP, examples include: "the best (i.e., most parsimonious) explanation
for statistical irregularities due to lexical affinity": what does
"parsimonious explanation", "lexical affinity" (S.1), or "explainedness"
of a node (S.3) mean? I would like to see a more formal definition right
where this concepts are introduced.

The word "parsimonious" is used here in its typical, non-technical sense to refer to explanations which cover the data and yet are as simple as possible. It's used in the introduction, and is just intended to give a sense to the reader of what is to come, in terms of the logic of the model. Since its not a term, nor doesn't pretend to be, we don't see the problem.

We have excised the term "lexical affinity", which was intend to point at the predictability that remains after
syntactic predictability is removed in the denominator of LPR, but is admittedly rather cryptic in the introduciton, and is never returned to.

"Explainedness" gets an informal explanation just after its introduction in Section 3, and then more formal definition
later (3.3). An earlier draft had expainedness defined immediately, but this required forward pointers to node interaction functions, which the other reviewers disliked. There's a certain amount of interconnectedness here that
makes it impossible to fully satisfy the need to define everything formally up front.

> - Section 2: I found the discussion of formulaic sequence vs. multi-word
generally interesting but could not understand how this distinction
plays a role in the task you are trying to address and the model you
present -- it is frustating for a reviewer to try to follow a one-page
discussion on exact terminology and then jump to the presentation of
related work by noticing that is not that important to understand it
("Regardless of the terminology used..."). An evil reviewer could think
that you try to account for FS because they are easier to handle in your
model: what would be the results on a FS vs. MWE dataset?

"Regardless of the terminology used..." is not intended to imply that the terminology is not
important, just that basic methodologes used for multiword lexicon creation are somewhat
independant of them. We have reworded this.

The point of that section is to be clear about what we are doing, and how it relates to other work in NLP,
where the default term for the targets of this sort of extraction is MWE. The fact that semantic 
non-compositionality is not core to the definition of FS is in fact very important in terms of 
the model we have built. The FS versus MWE distinction is quite important relevant to the motivation 
discussed at the end of that section.

In the discussion, we briefly consider exactly the FS versus MWE distinction you mention.
The answer is that our model is quite good at identifying MWE (better than non-MWE FS),
but it will of course identify some non-MWE FS, and so applying it directly to MWE dataset 
would result in apparently low precision.

>- Section 3: there are a plethora of lexical association measures from
the literature, why using LPR? Also, why using the minimum LPR as
opposed to the product (Brooke et al., 2015). I found your explanation
in the paper rather tentative...

There are a plethora of lexical associations measures, but as we already note the the backgound section,
very few scale to gapped n-grams of unrestricted length (some have no formulation beyond two words, others do, but
are exponential in the statistics that must be collected as n increases). Those that do scale do quite poorly at the general task, as shown here with raw counts and PMI; as we mention in the experiment section, other work which has compared our baseline models here with a wider range of such measures. LPR was specifically designed for FS identification and showed good results in earlier, and in the last paragraph of Section 3.1, we very talk explicitly about why minLPR is the correct measure for this particular use (i.e. the lattice), where each step up a layer of the lattice involves adding a single word, which is what the minLPR metric is focusing on.

>- Section 3.2 why cherry-picking the threshold for hard covering to 2/3
or $C$ in the range [3, 6] as opposed to tune on dev data? Same for the
hyperparameter in the bullet list at the end of 3.4?

"Cherry-picking" suggests we are just picking the best values for our test set, which is certainly not the case. All of the hyperparameters you mention were in fact subject to some early evaluation on development data and then fixed from that point on. We did not rigorously tune them in the machine learning sense, which is perhaps what you mean by "cherry picking"; we wanted to avoid supervision as much as possible, and tuning of that kind is supervision; we picked reasonable values, saw that they worked, and moved on. We've removed the reference to [3 ,6] since it seems to have lead to this misinterpretation: we did some post hoc evaluation of what values of C caused the model performance to drop drastically, but that was unrelated to the selection of 4 as our C value, which happened very early in development.

>- Section 3.4: why not looking also at other node visiting strategies?
E.g., random?

We did test a few options on dev data (based on length and LPR; not random, though, because we wanted a deterministic model), and decided on count based sorting.

>- Section 4: there exists a plethora of datasets for MWE, why not
comparing with other datasets: how were the dataset chosen? Also, why
not using corpora for the same language of different sizes (cf. e.g.,
Riedl and Biemann)?

By datasets, do you mean MWE vocabularies? MWE corpora like the STREUSLE? We don't see what you mean, since no corpus annotated with MWE could possibly have the quanitity of data required to build an unsupervised model like this. In terms of evaluation, the main reason not to use existing MWE datasets is exactly that we are not doing MWE extraction, but rather FS extraction; the existing MWE datasets have at best very inconsistent treatment of nonMWE FS, generally. Though it is possible to use MWE datasets for FS evaluation, see Brooke et al. (2015) who derived a test set from STREUSLE, it requires some hackiness that we felt was indefensible for our main evaluation: we did include a small, targeted evaluation of recall using STREUSLE.  Anyway, we addressed this issue rather thoroughly in the previous reviewer response.

It is worth mentioning (and we've added a small note to the paper) that we do prefer social media and mixed genre corpora, which represent a much more interesting range of FS pheonomena. Since you mention Reidl and Bieman, one criticim we have of that work was that it was focused on extremely specific, technical corpora, and not particularly representative of general FS phenomena across the language as whole.

We in fact do have corpora of different sizes for English, namely the ICWSM and BNC. Perhaps you mean taking smaller
version of the same corpus and seeing the effect of data size? This would be interesting, but it's not a trivial addition, since our test sets are sampled from the corpus; subsampling the corpus would require creating new test sets for those corpus.

- Section 6: When discussing "the time needed to build and optimize the
lattice" it would be good to add exact run-time figures

This is a reasonable idea, but we don't feel entirely confident reporting exactly runtime features due to difficulty in creating a controlled environment (i.e. DP-seg takes over 10 days to run on the BNC, and we can't ensure that our server stays otherwise unused) as well as the fact we can't control for the implementation of the comparison techniques. Instead, we've hedged our discussion a bit.

### 2017-07-24 tacl.tex
First pass on second round fixes

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

@@

Despite over 25 years of research in computational linguistics aimed at acquiring multiword lexicons using corpora statistics, and growing evidence that speakers process language primarily in terms of memorized sequences \cite{Wray08}, the individual word nonetheless stubbornly remains the \textit{de facto} standard processing unit for most research in modern NLP. The potential of multiword knowledge to improve both the automatic processing of language as well as offer new understanding of human acquisition and usage of language is the primary motivator of this work. Here, we present an effective, expandable, and above all tractable new approach to comprehensive multiword lexicon acquisition. Our aim is to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14} and more sophisticated statistical models \cite{Newman12} that do not scale to the large corpora, the main source of the distributional information in modern NLP systems.

@@

A central challenge in building comprehensive multiword lexicons is paring down the huge space of possibilities without imposing restrictions which disregard a major portion of the multiword vocabulary of a language: allowing for diversity creates significant redundancy among statistically promising candidates. The lattice model proposed here addresses this primarily by having the candidates---contiguous and non-contiguous $n$-gram types---compete with each other based on subsumption and overlap relations to be selected as the best (\ie most parsimonious) explanation for statistical irregularities due to lexical affinity. We test this approach across four large corpora in three languages, including two relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms alternatives, offering scalability and many avenues for future enhancement.

@@

In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework. Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS inventory of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians. Note that the FS framework allows for individual morphemes be part of a formulaic sequence, but for practical reasons we focus primarily on lemmatized words as the unit out of which FS are built.

@@

Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has typically been lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}. When these methods are used to build a lexicon, particular binary syntactic patterns are typically chosen. Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words. Another measure which addresses sequences of longer than two words is the $c$-value \cite{Frantzi00} which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones. Mutual expectation \cite{Dias99} involves deriving a normalized statistic that reflects the extent to which a phrase resists the omission of any constituent word. Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase. Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure \cite{Riedl15} is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word.

@@

\termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram. If enough subsuming $n$-grams are on, then the shorter $n$-gram will be discounted to the extent that it will be turned off, preventing redundancy. This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $a_1,\dotts, a_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes). Then, the $\cover(t)$ score for a covered node $t$ is:
\begin{displaymath}
\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(a_i)}}{c(t)}\Big)
\end{displaymath}
When applied as an exponent to a minLPR score, it serves as simple, quick-to-calculate approximation of a new minLPR with the counts corresponding to the covering nodes removed from the calculation. The \cover score takes on values in the range 0 to 1, with 1 being the default when no covering occurs.

@@

A simple but effective solution which avoids extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(b_i)}\Big)}
\end{displaymath}
where $b_i$ is the $i$th clearing node of $t$, \ie turned-on nodes below $t$ in the lattice. We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5. Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs. Note that one major advantage with this particular formulation of clearing is that low-LPR nodes will be unable to clear higher LPR nodes above them in the lattice; otherwise, bad FS like \ex{of the} might be selected as FS based purely to increase the explainedness of the many $n$-grams they appear in.

@@

The third mechanism of node interaction involves $n$-grams which overlap in the corpus. In general, independent FS do not consistently overlap. For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR. To address this problem, rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes---a penalty rather than an incentive which expresses the model's confusion at having overlapping FS. Let $\mathit{oc}(x,y)$ be the number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to overlapping nodes, \ie turned-on nodes which overlap with target node $t$ in the corpus. We define $\overlap(t)$ as:
\begin{displaymath}
	\overlap(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{\mathit{oc}(t,o_i)}}
\end{displaymath}

@@

In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{\mathit{on}}(t)$ is 1 if node $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse. The objective function maximized by the model is then the explainedness ($\mathit{expl}$) across all the nodes of the lattice, $t_1,\dots,t_{|T|} \in T$, which can be defined in terms of minLPR and the node interaction functions:
%
\begin{multline}
	\mathit{expl}(T) = \prod_{i=1}^{|T|}{I_{\mathit{on}}(t_i)\cdot C^{-\overlap(t_1)}} \\ + I_{\mathit{off}}(t_i)\cdot\minLPR(t_i)^{-\cover(t_i) \cdot \clear(t_i)}
\end{multline}
\noindent
When a node is off, its explainedness is the inverse of its minLPR, except if there are covering or clearing nodes which explain it by pushing the exponent of minLPR towards zero. When the node is on, its explainedness is the inverse of a fixed cost hyperparameter $C$, though this cost is increased if it overlaps with other active nodes. 
All else being equal, when $\minLPR(t) > C$, a node will be selected as an FS, and so, independent of the node interactions, $C$ can be viewed as the threshold for the minLPR association measure under a traditional approach to MWE identification. There is no upper bound on $C$, but empirically, we have found values in the range $[3,6]$ give reasonable results for the languages presented in this paper.

@@

\begin{algorithm}[t!]
	\caption{Optimization algorithm. $T$ is an ordered list of the nodes in the lattice. Nodes (designated by $t$) contain pointers to the nodes immediately linked to them in the lattice. States (designated by $s$) indicate whether each node is $\mathrm{ON}$ or $\mathrm{OFF}$. Explainedness values are indicated by $e$.}
	\label{alg:opt}
	\begin{algorithmic}

	\Function{LocalOpt}{$s_{\mathit{start}}, t, T_{\mathit{rev}}, T_{\mathit{aff}}$}
		\State $s_{\mathit{start}} \gets \Call{Set}{s, t, \mathrm{ON}}$
		\State $Q \gets \Call{EmptyQueue}{\null}$
		\State $e_{\mathit{best}} \gets 0$
		\State $s_{\mathit{best}} \gets \mathrm{NULL}$
		\State $\Call{Push}{Q, s_{\mathit{start}}}$
		\Repeat
			\State $s_{\mathit{curr}} \gets \Call{Pop}{Q}$
			\State $e_{\mathit{curr}} \gets \Call{CalcExpl}{s_{\mathit{curr}}, T_{\mathit{aff}}}$
			\For{$t_{\mathit{rev}} \textrm{ in } T_{\mathit{rev}}$}
					\State $s_{\mathit{new}} \gets \Call{Set}{s_{\mathit{curr}},t_{\mathit{rev}}, \mathrm{OFF}}$
					\State $e_{\mathit{new}} \gets\Call{CalcExpl}{s_{\mathit{new}}, T_{\mathit{aff}}}$
					\If{$ e_{\mathit{new}} > e_{\mathit{curr}}$}

					\State $\Call{Push}{Q, s_{\mathit{new}}}$
					\If{$e_{\mathit{new}} > e_{\mathit{best}}}$:
						\State $e_{\mathit{best}} \gets e_{\mathit{new}}$
							\State $s_{\mathit{best}} \gets s_{\mathit{new}}$
					\EndIf
					\EndIf
				\EndFor
		\Until{$\Call{IsEmpty}{Q}$}
	\State \Return $s_{\mathit{best}}$
	\EndFunction
\State
\State $\Call{FrequencySortReverse}{T}$
\State $s \gets \Call{InitializeAllOff}{T}$
\Repeat
	\State $\mathit{Changed} \gets \mathrm{FALSE}$
		\For{$t \textrm{ in } T$}
		\State $T_{\mathit{rev}} \gets \Call{GetRelevant}{t,T}$
		\State $T_{\mathit{aff}} \gets \Call{GetAffected}{T_{\mathit{rev}},T}$
		\State $s_{\mathit{new}} \gets \Call{LocalOpt}{s,t,T_{\mathit{rev}},T_{\mathit{aff}}}$
		\If{$s_{\mathit{new}} \neq s$}
			\State $s \gets s_{\mathit{new}}$
			\State $\mathit{Changed} \gets \mathrm{TRUE}$
		\EndIf
		\EndFor
\Until{$!\mathit{Changed}$}
\end{algorithmic}
\end{algorithm}

The dependence of the explainedness of nodes on their neighbors effectively prohibits a global optimization of the lattice. Fortunately, though most of the nodes in the lattice are part of a single connected graph, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions. The main optimization loop consists of iterations over the lattice until complete convergence (no changes in the final iteration). For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice. The order that we perform this has an effect on the result: among the obvious options, good results are obtained through ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams.

@@

				Lattice & \bf{0.67} & 0.44 & \bf{0.54} & & \bf{0.38}& 0.58 & \bf{0.46} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
            \bottomrule

>>>>

      \author{Julian Brooke \qquad Timothy Baldwin \\ Computing and Information Systems \\ The University of Melbourne \\ \url{julian.brooke@gmail.com} \\ \url{tb@ldwin.net}
 \And               Jan Snajder\\
Electrical Engineering and Computing \\
 University of Zagreb \\
  {\tt jan.snajder@fer.hr}}

	\\}

@@

Despite over 25 years of research in computational linguistics aimed at acquiring multiword lexicons using corpora statistics, and growing evidence that speakers process language primarily in terms of memorized sequences \cite{Wray08}, the individual word nonetheless stubbornly remains the \textit{de facto} standard processing unit for most research in modern NLP. The potential of multiword knowledge to improve both the automatic processing of language as well as offer new understanding of human acquisition and usage of language is the primary motivator of this work. Here, we present an effective, expandable, and tractable new approach to comprehensive multiword lexicon acquisition. Our aim is to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14} and more sophisticated statistical models \cite{Newman12} that do not scale to large corpora, the main source of the distributional information in modern NLP systems.

@@

A central challenge in building comprehensive multiword lexicons is paring down the huge space of possibilities without imposing restrictions which disregard a major portion of the multiword vocabulary of a language: allowing for diversity creates significant redundancy among statistically promising candidates. The lattice model proposed here addresses this primarily by having the candidates---contiguous and non-contiguous $n$-gram types---compete with each other based on subsumption and overlap relations to be selected as the best (\ie most parsimonious) explanation for statistical irregularities. We test this approach across four large corpora in three languages, including two relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms alternatives, offering scalability and many avenues for future enhancement.

@@

In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework. Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS inventory of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians. Note that the FS framework allows for individual morphemes to be part of a formulaic sequence, but for practical reasons we focus primarily on lemmatized words as the unit out of which FS are built.

@@

From a practical perspective, the starting point for multiword lexicon creation has typically been lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}. When these methods are used to build a lexicon, particular binary syntactic patterns are typically chosen. Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words. Another measure which addresses sequences of longer than two words is the $c$-value \cite{Frantzi00} which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones. Mutual expectation \cite{Dias99} involves deriving a normalized statistic that reflects the extent to which a phrase resists the omission of any constituent word. Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase. Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure \cite{Riedl15} is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word.

@@

\termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance} and \ex{keep it under your hat}), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram. If enough subsuming $n$-grams are on, then the shorter $n$-gram will be discounted to the extent that it will be turned off, preventing redundancy. This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, $y_i$ the current FS status for node $x_i$ (0 if off, 1 if on) and $ab(x)$ a function which produces the set of indicies of all nodes above node $x$ in the lattice. Then, the $\cover(x_t)$ score for a covered node $t$ is:
\begin{displaymath}
\cover(x_t) = \max\Big(0,\frac{c(x_t) - \sum_{i \in ab(x_t)}y_i\cdot{c(x_i)}}{c(x_t)}\Big)
\end{displaymath}
When applied as an exponent to a minLPR score, it serves as simple, quick-to-calculate approximation of a new minLPR with the counts corresponding to the covering nodes removed from the calculation. The \cover score takes on values in the range 0 to 1, with 1 being the default when no covering occurs.

@@

A simple but effective solution which avoids extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(x_t) = \prod_{i \in bl(x_t)}{\min\Big(1,\frac{\minLPR(x_t)}{y_i\cdot\minLPR(x_i)}\Big)}
\end{displaymath}
where $bl(x_t)$ produces a set of indicies of nodes below $x_t$ in the lattice. We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(x_t)$ will be 0.5. Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs. Note that one major advantage with this particular formulation of clearing is that low-LPR nodes will be unable to clear higher LPR nodes above them in the lattice; otherwise, bad FS like \ex{of the} might be selected as FS based purely to increase the explainedness of the many $n$-grams they appear in.

@@

The third mechanism of node interaction involves $n$-grams which overlap in the corpus. In general, independent FS do not consistently overlap. For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR. To address this problem, rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes---a penalty rather than an incentive which expresses the model's confusion at having overlapping FS. For non-subsuming nodes $x_i$ and $x_j$, let $\mathit{oc}(x_i,x_j)$ be the count of instances of $x_i$ which contain at least one non-gap token of an corresponding instance of $x_j$. For subsuming nodes, though, overlap is treated asymmetrically, with $\mathit{oc}(x_i,x_j)$ equal to $c(x_j)$ (the lower count) if $j \in ab(x_i)$, but zero if $j \in bl(x_i)$.  Given this definition of $\mathit{oc}$, we define $\overlap(x_t)$ as:
\begin{displaymath}
	\overlap(x_t) = \frac{c(x_t)}{c(x_t) - \sum_{i=1}^{|X|}{y_i\cdot\mathit{oc}(x_t,x_i)}}
\end{displaymath}

@@

The objective function maximized by the model is then the explainedness ($\mathit{expl}$) across all the nodes of the lattice $X$, $x_i,\dots,x_{N}$, which can be defined in terms of minLPR and the node interaction functions:
%
\begin{multline}
	\mathit{expl}(X) = \prod_{i=1}^{|X|}{y_i\cdot C^{-\overlap(x_i)}} \\ + (-y_i + 1)\cdot\minLPR(x_i)^{-\cover(x_i) \cdot \clear(x_i)}
\end{multline}
\noindent
When a node is off, its explainedness is the inverse of its minLPR, except if there are covering or clearing nodes which explain it by pushing the exponent of minLPR towards zero. When the node is on, its explainedness is the inverse of a fixed cost hyperparameter $C$, though this cost is increased if it overlaps with other active nodes.  All else being equal, when $\minLPR(t) > C$, a node will be selected as an FS, and so, independent of the node interactions, $C$ can be viewed as the threshold for the minLPR association measure under a traditional approach to MWE identification.

@@

\begin{algorithm}[t!]
	\caption{Optimization algorithm. $X$ is an ordered list of the nodes in the lattice. Nodes (designated by $x$) contain pointers to the nodes immediately linked to them in the lattice. States (designated by $Y$) indicate whether each node is $\mathrm{ON}$ or $\mathrm{OFF}$. Explainedness values are indicated by $e$. rev=relevant, aff=affected, curr=current}
	\label{alg:opt}
	\begin{algorithmic}

	\Function{LocalOpt}{$Y_{\mathit{start}}, x, X_{\mathit{rev}}, X_{\mathit{aff}}$}
		\State $Y_{\mathit{start}} \gets \Call{Set}{Y_{\mathit{start}}, x, \mathrm{ON}}$
		\State $Q \gets \Call{EmptyQueue}{\null}$
		\State $e_{\mathit{best}} \gets 0$
		\State $Y_{\mathit{best}} \gets \mathrm{NULL}$
		\State $\Call{Push}{Q, Y_{\mathit{start}}}$
		\Repeat
			\State $Y_{\mathit{curr}} \gets \Call{Pop}{Q}$
			\State $e_{\mathit{curr}} \gets \Call{CalcExpl}{Y_{\mathit{curr}}, X_{\mathit{aff}}}$
			\For{$x_{\mathit{rev}} \textrm{ in } X_{\mathit{rev}}$}
					\State $Y_{\mathit{new}} \gets \Call{Set}{Y_{\mathit{curr}},x_{\mathit{rev}}, \mathrm{OFF}}$
					\State $e_{\mathit{new}} \gets\Call{CalcExpl}{s_{\mathit{new}}, X_{\mathit{aff}}}$
					\If{$ e_{\mathit{new}} > e_{\mathit{curr}}$}

					\State $\Call{Push}{Q, Y_{\mathit{new}}}$
					\If{$e_{\mathit{new}} > e_{\mathit{best}}}$:
						\State $e_{\mathit{best}} \gets e_{\mathit{new}}$
							\State $Y_{\mathit{best}} \gets Y_{\mathit{new}}$
					\EndIf
					\EndIf
				\EndFor
		\Until{$\Call{IsEmpty}{Q}$}
	\State \Return $Y_{\mathit{best}}$
	\EndFunction
\State
\State $\Call{FrequencySortReverse}{X}$
\State $s \gets \Call{InitializeAllOff}{X}$
\Repeat
	\State $\mathit{Changed} \gets \mathrm{FALSE}$
		\For{$x \textrm{ in } X$}
		\State $X_{\mathit{rev}} \gets \Call{GetRelevant}{x,X}$
		\State $X_{\mathit{aff}} \gets \Call{GetAffected}{X_{\mathit{rev}},X}$
		\State $Y_{\mathit{new}} \gets \Call{LocalOpt}{Y,x,X_{\mathit{rev}},X_{\mathit{aff}}}$
		\If{$Y_{\mathit{new}} \neq Y$}
			\State $Y \gets Y_{\mathit{new}}$
			\State $\mathit{Changed} \gets \mathrm{TRUE}$
		\EndIf
		\EndFor
\Until{$!\mathit{Changed}$}
\end{algorithmic}
\end{algorithm}

The dependence of the explainedness of nodes on their neighbors effectively prohibits a global optimization of the lattice. Fortunately, though most of the nodes in the lattice are part of a single connected graph, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions. The main optimization loop consists of iterations over the lattice until complete convergence (no changes in the final iteration). For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice. The order that we perform this has an effect on the result: among the obvious options (LPR, $n$-gram length), in development good results were obtained through ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams.

@@

				Lattice & \bf{0.67} & 0.45 & \bf{0.54} & & \bf{0.38}& 0.58 & \bf{0.46} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
            \bottomrule
